Positional entropy in childes

### 2018-09-10 Unigram Positional Entropy.Rmd
letter entropies and touches

```{r setup, include = FALSE}
# load packages
library(knitr)
library(tidyverse)
library(directlabels)
library(childesr) #data
library(SnowballC) #stemmer
library(tidytext)
library(entropy)
library(tidyboot)
library(dplyr)
library(tokenizers)
library(tau)
library(reticulate)
knitr::opts_chunk$set(echo = TRUE)

>>>>

```{r setup, include = FALSE}
# load packages
library(knitr)
library(tidyverse)
library(directlabels)
library(childesr) #data
library(SnowballC) #stemmer
library(tidytext)
library(entropy)
library(tidyboot)
library(dplyr)
library(tokenizers)
library(tau)
knitr::opts_chunk$set(echo = TRUE)

### 2018-09-10 letter_entropy.Rmd
letter entropies and touches

---
title: Letter entropy in childes
author: Joe Klafka
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: false
    number_sections: false
    theme: lumen
    toc_float: false
    code_folding: show 
---

@@

  # 
  # 
  # ggplot(adult_utterances, aes(x = length)) +
  #   geom_histogram(fill = "white", color = "black")

@@

  map(1:10, ~letter_entropy(letter_counts, .x)) 
}

@@

>>>>

---
title: By-letter entropy in childes
author: Joe Klafka
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: false
    number_sections: false
    theme: lumen
    toc_float: false
    code_folding: show 
---

@@

@@

  map(1:10, ~letter_entropy(letter_counts, .x)) ##first 10 letters, after this entropy shrunk close to 0
}

@@

prov_child_letters <- map(2:10, ~get_letter_entropies("Target_Child", .x, prov_utterances)) #list of lists of lists

### 2018-09-10 nonenglish_ce&mi.Rmd
letter entropies and touches

---
title: "Untitled"
author: "Joe Klafka"
date: "8/28/2018"
output: html_document
---

>>>>

---
title: Non-English Conditional Entropy and Mutual Information
author: Joe Klafka
date: "`r Sys.date()`"
output: 
  html_document:
    toc: false
    number_sections: false
    theme: lumen
    toc_float: false
    code_folding: show 
---

### 2018-09-10 positional_entropy_childes.Rmd
letter entropies and touches

@@

ggplot(ce[[3]], aes(x = X, y = ce, color = as.factor(Y))) + 
  facet_wrap(~ length) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Conditional entropy vs. conditioned random variable (utterances of length 5)")

>>>>

counts <- map(2:8, ~get_counts("not child", .x, prov_utterances))

@@

ggplot(ce_br, aes(x = X, y = ce, color = as.factor(Y))) + 
  facet_wrap(~ length) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Conditional entropy vs. conditioned random variable")
